Kinetic Modeling of Isobutane Alkylation with Mixed C4 Olefins and Sulfuric Acid as Catalyst Using the Asynchronous Global Optimization Algorithm

### 2021-12-14 2022/PAVT/PAVT2022.tex
UNN part of Experiments

Согласно постановкам задач (\ref{eq:objective_func1}) и (\ref{eq:objective_func2}) в данной работе были проводились соответсвующие расчеты.

%ННГУ
Для проведения численных экспериментов использовался UNN supercomputer Lobachevsky (CentOS 7.2, SLURM, two CPU Intel Sandy Bridge E5-2660 2.2 GHz and 64 Gb RAM on the node). Асинхронный алгоритм глобальной оптмизации был реализован на C++ (GCC 5.5.0 and Intel MPI were used); вычисление значений целевой функции было реализовано в Python 3.9.

@@

%ННГУ
Для оценки эффективности реализованного метода оптимизации было проведено сравнение результатов работы последовательного, параллельного синхронного и параллельного асинхронного алгоритмов с использованием 8 nodes при решении задачи в данной постановке. В таблице \ref{table_30D} приведены минимальные значения objective function, найденные соответствующими методами, время решения задачи (в часах) и ускорение по времени. При запуске был использован параметр метода $r=3.0$ из (\ref{R}) и точность $\epsilon = 10^{-2}\left\|b-a\right\|$ в критерии остановки. После достижения методом глобального поиска заданной точности решение уточнялось Hook-Jeeves local method \cite{HookJeeves} с точностью $\epsilon = 10^{-4}\left\|b-a\right\|$.

@@

Результаты показывают, что оба параллельных алгоритма показали невысокое ускорение, но нашли более хорошее решение, чем последовательный метод. При этом асинхронный алгоритм нашел лучшее решение, чем синхронный. Это также объясняет и меньшее  ускорение асинхронного алгоритма по сравнению с синхронным, т.к. асинхронный метод провел больше испытаний в процессе поиска оптимальных кинетических параметров задачи.

@@

%ННГУ
При решении данной задачи также было проведено сравнение работы последовательного, параллельного синхронного и параллельного асинхронного алгоритмов. 
В таблице \ref{table_15D} приведены минимальные значения целевой функции, найденные соответствующими методами, время решения задачи (в часах) и ускорение по времени при использовании 8 nodes. Все параметры метода были аналогичны предыдущему запуску.

@@

Результаты показывают, что все алгоритмы находят хорошее по значению целевой функции решение. При этом асинхронный алгоритм демонстрирует в два раза большее ускорение, чем синхронный. Хорошее ускорение асинхронного алгоритма сохраняется и при большем числе узлов, результаты его работы приведены в таблице \ref{tab_parall}.

>>>>

Согласно постановкам задач (\ref{eq:objective_func1}) и (\ref{eq:objective_func2}) в данной работе были проводились соответсвующие расчеты.
%ННГУ
To carry out the numerical experiments, UNN supercomputer Lobachevsky was used (CentOS 7.2, SLURM, two CPU Intel Sandy Bridge E5-2660 2.2 GHz and 64 Gb RAM on the node). The asynchronous global optimization algorithm was implemented using C++ (GCC 5.5.0 and Intel MPI were used); the objective function values were computed using Python 3.9.

@@

%ННГУ
To evaluate the efficiency of the implemented optimization method, the results obtained using the sequential algorithm, the parallel synchronous, and the parallel asynchronous ones with the use of 8 nodes when solving the problem in the above statement were compared.  
The minimum values of the objective function found by respective methods, the times of solving the problem (in hours), and the values of speedup in time are presented in Table \ref{table_30D}. 
During the experiments the parameter of the method $r=3.0$ from (\ref{R}) and the accuracy  $\epsilon = 10^{-2}\left\|b-a\right\|$ in the termination condition were used. Once the global search method achieves the preset accuracy, the solution was refined by Hook-Jeeves local method \cite{HookJeeves} with the accuracy $\epsilon = 10^{-4}\left\|b-a\right\|$.

@@

The results have shown that both parallel algorithms had demonstrated a moderate speedup but had found better solutions than the sequential method. At that, the asynchronous algorithm had found a better solution than synchronous one. This explains also a smaller speedup of the asynchronous algorithm as compared with the synchronous one since the asynchronous method had executed more trials in the course of search for the optimal kinetic parameters of the problem.

@@

%ННГУ
When solving this problem, the operation performances of the sequential algorithm, of the parallel synchronous, and of the parallel asynchronous ones were also compared.  
The minimum values of the objective function found by respective methods, the time of solving the problem (in hours), and the speedup in time with the use of 8 nodes are presented in Table \ref{table_15D}. All the parameters of the method were the same as in the previous run.

@@

The results have shown that all algorithms had found good solutions (in the values of the objective function). At that, the asynchronous algorithm had demonstrated two times higher speedup than the synchronous one. A good speedup of the asynchronous algorithm remains at a greater number of nodes as well, the results of its work are presented in Table \ref{tab_parall}.
